Assigning Scouts to Optimal Patrols

### 2016-06-08 draft1.tex
some edits

\section*{Mathematical Model}
To model the relationships between scouts, we use a mathematical graph. A graph is a convenient way to illustrate direct relationships between pairs of objects; for example, if we have a collection of cities in a state, a city can be related to another if there is a road between them. A city can be considered a vertex, and two cities can have a edge between them if there is a road connecting them. Edges can have weights attached to them such as the length of the road between the two cities. The edges can even be directed, meaning that distance from City A to City B might be different with the distance from City B to City A (two one-way roads may have different lengths). Graphs can also be complete if each vertex in a graph is connected to every other vertex. Graphs are not limited to just cities on a map, but rather a collection of objects with any notion of relationship can be represented as a graph.

For our problem, we let the scouts be vertices in our graph. A directed edge between Scout A and Scout B has a weight proportional to how much Scout A likes Scout B. A partition of a graph is a grouping of vertices, thus a partition of scouts is considered a troop. Whenever our graph is arranged into two partitions, we then can assess this arrangement based on a scoring criterion (or an objective function). We would like to find a partition of the vertices in the graph that either minimizes or maximizes an objective function given constraints on the sizes of subsets generated by our partition. This results in a complete, directed graph on 13 vertices having edge weights 0, 1, or -1, corresponding to indifference, approval, or disapproval, respectively. Scoutmaster Bruce specifically would like two patrols from the 13 scouts - one of size 6, the other of size 7. The total number of partitions given these constrants is $\binom{13}{6} = \binom{13}{7} = 1716$. This number is reasonable enough that we may calculate the total loss of every valid grouping and select the partition with the lowest or highest score depending on the objective function.

We measure the goodness (or score) of a partition in six different ways, corresponding to six different objective functions, which we dub MinCut, FriendCut, EnemyCut, AwkwardCut, and HybridCut. MinCut is designed to minimize the cut edge weights between partitions (see \textit{Solution of Mathematical Problem}). FriendCut is designed to maximize the number of intra-patrol positive edge weights. EnemyCut is meant to minimize the number of intra-patrol negative edge weights, Awkward cut ($+i$) is the same as MinCut, but with an additional penalty of $i$ if there are a pair of scouts, Scout A and Scout B, such that Scout A favors Scout B, but Scout B disfavors Scout A. HybridCut is a convex combination of MinCut and FriendCut, each with equal weight (that is, half the MinCut loss plus half the FriendCut loss). Our three primary objective functions - MinCut, FriendCut, and EnemyCut are given a more rigorous treatment in the next section.

>>>>

\section*{Mathematical Model}
To model the relationships between scouts, we use a mathematical graph. A graph is a convenient way to illustrate direct relationships between pairs of objects; and a good example that explains how they work is to consider roads between cities. On a map, we consider two cities to be ``connected" if they share a road between them; by this, we mean that the existence of a road defines the property of two cities being connected. Graphs abstract this notion; instead of considering connections between a map of cities, we consider connections between groups of any kind of object. In graph theoretic terminology, we call these objects vertices, and the entity that connects two vertices is called an edge. We could redefine our map of cities in this terminology: consider cities as being vertices in a graph where the criterion for having an edge between two vertices is when there is a road built between the cities. Another common optional property of graphs is where we ascribe numbers to the edges, corresponding to particular ``weights" that they have. In our city graph example, we could consider each edge to have a weight of how long the road is. Edges can even be directed, meaning that a particular relationship between vertices is only valid from one vertex to another, and not the other way around. For example, there could be a one-way road from city A to city B, and no road from city B to city A. In our situation, we will also consider graphs that are complete, where completeness means that each vertex is connected to every other vertex.

For our problem, we can define a graph where scouts are vertices. A directed edge between Scout A and Scout B has a weight proportional to how much Scout A likes Scout B. We give the directed edge between scout A and scout B a weighting of 1 if A likes B, 0 if A is indifferent to B, and a -1 if A disapproves of B. This results in a complete, directed graph of 13 vertices, since there are 13 scouts. Note that these edges are directed; we want to consider cases where the relationship between two scouts is not symmetric, whereas a weighted undirected graph would not be able to represent this asymmetry. Let us now define a $k$-partition of a graph as a grouping of vertices where each vertex is assigned into one of $k$ groups where $k$ is a natural number; thus, a $k$-partition of the vertices in the scout graph would represent splitting up the scouts into $k$ different patrols. Scoutmaster Bruce specifically would like two patrols from the 13 scouts - one of size 6, the other of size 7, which means that we need to find a 2-partition of the graph where 6 vertices are in one grouping and 7 are in the other. The total number of partitions given these constraints is $\binom{13}{6} = \binom{13}{7} = 1716$. Given these 1716 partitions, we want to select one of them that is ``best" for the scouts in question. In mathematics, picking the ``best" option out of a list of options corresponds to first defining a function that ``scores" how good an item is (or bad an item is) and then picking the item with the highest score (or the least score, if our scoring function defines how bad an item is). This process of selecting the item from a list that has the most extreme score is called optimization. From now on, we will call these scoring functions objective functions. Our process for optimizing a partition of the scouts will become computing an objective function for each possible partition and then selecting the partition that gives us the most extreme score. This ``brute force" approach to computing the scores isn't always appropriate for optimizing an objective function over a set of values, as the size of the set of values is too large for a computer to iterate over in a timely fashion. Often, a more sophisticated technique will be required to iterate over a manageable subset of the set of possible values. However, 1716 is within the range of sizes of sets to iterate over where we could apply a brute force technique to solve for the most optimal partition.

We provide six different objective functions that we deemed reasonable for measuring how well patrol partitions would work. We dub each of these functions MinCut, FriendCut, EnemyCut, AwkwardCut (+1), AwkwardCut (+2), and HybridCut. MinCut is designed to minimize the cut edge weights between partitions (see \textit{Solution of Mathematical Problem}). FriendCut is designed to maximize the number of intra-patrol positive edge weights. EnemyCut is meant to minimize the number of intra-patrol negative edge weights, Awkward cut ($+i$) is the same as MinCut, but with an additional penalty of $i$ if there are a pair of scouts, Scout A and Scout B, such that Scout A favors Scout B, but Scout B disfavors Scout A. HybridCut is a convex combination of MinCut and FriendCut, each with equal weight (that is, half the MinCut loss plus half the FriendCut loss). Our three primary objective functions - MinCut, FriendCut, and EnemyCut are given a more rigorous treatment in the next section.
